% \documentclass[a4paper,12pt]{article}
% \usepackage[utf8]{inputenc}
% \usepackage[margin=1in]{geometry}
% \usepackage[table]{xcolor} 
% \usepackage{longtable} 
% \usepackage{booktabs}  

% \title{\textbf{Assignment 8: Parallel vs. Distributed Systems}}
% \author{Sparsh Shakya, BETN1AI24036}
% \date{\today}

% % \begin{document}

% \maketitle

\subsection{Introduction}
Modern computing relies on two main architectural paradigms: Parallel Systems, which optimize performance within a single machine, and Distributed Systems, which provide scalability across global networks.

\subsection{Comparison of System Features}

\renewcommand{\arraystretch}{2} 
\begin{longtable}{|p{3.5cm}|p{5cm}|p{5cm}|}
\hline
\rowcolor{gray!20} \textbf{Feature} & \textbf{Parallel System (NVIDIA CUDA)} & \textbf{Distributed System (Google Spanner)} \\ \hline
\endfirsthead 

\hline
\rowcolor{gray!20} \textbf{Feature} & \textbf{Parallel System (NVIDIA CUDA)} & \textbf{Distributed System (Google Spanner)} \\ \hline
\endhead 

\textbf{Architecture} & Tightly coupled; thousands of cores in one GPU. & Loosely coupled; thousands of servers in different data centers. \\ \hline

\textbf{Memory} & \textbf{Shared Memory:} All cores share the same VRAM. & \textbf{Independent Memory:} Each server has its own RAM/Storage. \\ \hline

\textbf{Communication} & High-speed internal bus (NVLink/PCIe). & Network protocols (TCP/IP, RPC) over the internet. \\ \hline

\textbf{Scalability} & Vertical (Adding a more powerful GPU). & Horizontal (Adding more servers to the cluster). \\ \hline

\textbf{Fault Tolerance} & Low; if the GPU fails, the whole task stops. & High; if one server fails, others take over immediately. \\ \hline

\textbf{Primary Goal} & \textbf{Speed:} Solving complex math problems faster. & \textbf{Reliability:} Managing global data without downtime. \\ \hline

\end{longtable}



% \end{document}