
\subsection{Introduction}
The Operating System acts as a manager of resources. It performs several critical functions to ensure that hardware and software work together efficiently without conflicts.

\subsection{Operating System Functions}

\renewcommand{\arraystretch}{1.8} % Adds vertical padding for readability
\small 

\begin{longtable}{|p{3.2cm}|p{4.8cm}|p{5.5cm}|}
\hline
\rowcolor{gray!20} \textbf{Function} & \textbf{Description} & \textbf{Key Responsibilities} \\ \hline
\endfirsthead

\hline
\rowcolor{gray!20} \textbf{Function} & \textbf{Description} & \textbf{Key Responsibilities} \\ \hline
\endhead

\textbf{Process Management} & Manages the creation, scheduling, and deletion of processes. It ensures each process gets enough CPU time. & Creating/deleting processes, CPU scheduling, and synchronization. \\ \hline

\textbf{Memory Management} & Tracks every memory location (RAM). it decides which process gets memory, how much it gets, and when to free it. & Tracking used/free space, allocating memory to programs, and swapping data to disk. \\ \hline

\textbf{File Management} & Manages how data is stored in files and directories. It handles tasks like creating, deleting, and searching for files. & Creating directories, managing file permissions, and tracking file locations. \\ \hline

\textbf{Device Management} & Communicates with hardware devices (like printers or disks) through their respective drivers. & Managing input/output (I/O) devices like keyboards, printers, and monitors. \\ \hline

\textbf{Security \& Protection} & Protects data and programs from unauthorized access through passwords and similar techniques. & User authentication (passwords), firewalls, and process isolation. \\ \hline

\textbf{User Interface (UI)} & Providing a way for the user to interact with the hardware. & Managing the Graphical User Interface (GUI) or Command Line Interface (CLI). \\ \hline

\textbf{Error Detection} & Constantly monitors the system for crashes or hardware failures and provides alerts or recovery options. & Generating logs, debugging alerts, and preventing system crashes. \\ \hline

\textbf{Job Accounting} & Keeps track of time and resources used by various jobs and users for performance monitoring. & Monitoring CPU usage and storage limits for different user accounts. \\ \hline

\end{longtable}

% \end{document}